\LARGE \bf Thymio, an example of open source hardware robot \\ for formal education

### 2016-03-31 paper_ram.tex
modifs Michael

\begin{figure}
   \centering
	\includegraphics[width=.6\columnwidth]{figures/front_2016}
	\vskip 1.5em
	\includegraphics[width=\columnwidth]{figures/Thymio_II_sensors-actuators-eng}
	\caption{The Thymio robot and its main components.}
	\label{fig:schematique}
\end{figure}

@@

\begin{table}
\centering
\begin{tabularx}{\columnwidth}{ll}
\toprule
Description & Price (USD)\\
\midrule
electronic components & 15\,\$ \\
microcontroller & 4 \$ \\
motors & 2 \$ \\
plastic parts (hull, wheels, and light guides) & 4 \$ \\
assembling & 8 \$ \\
transport & 2 \$ \\
\bottomrule
Total & 35 \$ \\
\end{tabularx}
\caption{Production cost of Thymio.}
\label{tbl:thymio-price}
\end{table}

@@

Many existing robots need to be built or configured before having the first operational behavior. 
This is a barrier for many users and we wanted to avoid it carefully, having a robot able to show interesting behaviors right out of the box.
Therefore Thymio provides 6 different basic behaviors (see table \ref{tbl:basic-behaviors}), which are accessible as soon as the robot is started.
These allow people encountering Thymio for the first time to immediately interact with it, while providing insights into the many possibilities of the robot.
The behaviors are interactive and oriented towards the user. % SM: FIXME: not clear what "oriented towards the user" means
For each behavior, the robot's body has a different color, allowing the user to easily recognize it.
The user can navigate between the colors with the buttons and select the behavior she/he wants to use.
Basic behaviors can be exploited in a construction to create reactivity without the use of programming (see Figure~\ref{fig:example-construction}, the top four paper creations can be used with basic behaviors).

@@

The very specific structure of an open project has also drawbacks. 
Asked about problems met in their project (see Figure~\ref{fig:problems}), the participants to our survey mention the management of the community, the evolution of the project, the efforts in documentation, production and distribution and the limited resources.
There are here two kind of problems: one of management of people, the other in the development of the project after the first design.
The management of the project seems a recurrent problem and is related to the nature of this type of structure, mainly very flat and built on academic people with engineering background. 
Most of the projects, following our survey, are managed by the founder of the initiative and not by the most expert in the field or by a manager, which is perhaps not the best objective choice.
It is indeed very difficult to evolve from a phase where the engineering is the core of the project, to a new phase where communication and management play an increasing role.
The same holds for several other factors, like the efforts in documentation, production and distribution of the product. 
Also here there is a change of activity from the very creative and appealing design phase, to a phase of documentation and, in some cases, production and distribution which is not at all the same type of activity and requires different skills.
This shift requires extra efforts and motivation, which are often missing, especially for activities like documentation that are not appreciated by engineers.
In general many respondents to our survey identified the evolution of the project as a general problematic issue, which summarizes the several aspects mentioned above.

>>>>

\begin{figure}
   \centering
	\includegraphics[width=.8\columnwidth]{figures/front_2016}
	\vskip 1.5em
	\includegraphics[width=\columnwidth]{figures/wirelessThymioVecto}
	\caption{The Thymio robot and its main components for the Wireless and the plain version.}
	\label{fig:schematique}
\end{figure}

@@

\begin{table}
\centering
\begin{tabularx}{\columnwidth}{ll}
\toprule
Description & Price (USD)\\
\midrule
electronic components & 15\,\$ \\
microcontroller & 4 \$ \\
motors & 2 \$ \\
plastic parts (hull, wheels, and light guides) & 4 \$ \\
assembling & 8 \$ \\
transport & 2 \$ \\
\bottomrule
Total & 35 \$ \\
\end{tabularx}
\caption{Production cost of basic Thymio (without wireless modules).}
\label{tbl:thymio-price}
\end{table}

@@

Many existing robots need to be built or configured before having the first operational behavior. 
This is a barrier for many users and we wanted to avoid it carefully, having a robot able to show interesting behaviors right out of the box.
Therefore Thymio provides 6 different basic behaviors (see table \ref{tbl:basic-behaviors}), which are accessible as soon as the robot is started and are stored in flash permanently, also if the Thymio is reprogrammed by the user.
These basic behaviors allow people starting Thymio to immediately interact with it, while illustrating the many possibilities of the robot.
The behaviors are interactive and oriented towards the user. % SM: FIXME: not clear what "oriented towards the user" means
For each behavior, the robot's body has a different color, allowing the user to easily recognize it.
The user can navigate between the colors with the buttons and select the behavior she/he wants to use.
Basic behaviors can be exploited in a construction to create reactivity without the use of programming (see Figure~\ref{fig:example-construction}, the top four paper creations can be used with basic behaviors).

@@

The very specific structure of an open project has also drawbacks. 
Asked about problems met in their project (see Figure~\ref{fig:problems}), the participants to our survey mention the management of the community, the evolution of the project, the efforts in documentation, production and distribution and the limited resources.
There are here two kind of problems: one of management of people, the other in the development of the project after the first design.
The management of the project seems a recurrent problem and is related to the nature of this type of structure, mainly very flat and built on academic people with engineering background. 
More than 62\% of the answers to our survey report about projects that are managed by the founder of the initiative and not by the most expert in the field or by a manager, which is perhaps not the best objective choice.
It is indeed very difficult to evolve from a phase where the engineering is the core of the project, to a new phase where communication and management play an increasing role.
The same holds for several other factors, like the efforts in documentation, production and distribution of the product. 
Also here there is a change of activity from the very creative and appealing design phase, to a phase of documentation and, in some cases, production and distribution which is not at all the same type of activity and requires different skills.
This shift requires extra efforts and motivation, which are often missing, especially for activities like documentation that are not appreciated by engineers.
In general many respondents to our survey identified the evolution of the project as a general problematic issue, which summarizes the several aspects mentioned above.
